RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
formulated a bit more carefully: the prefix identifies a namespace, which here has a URL location (e.g. it's not an URN), which we can visit so that we may learn about the modificationDate predicate
request for clarification: can we use undefined prefixes?

From the list of namespaces in `prefixes`, we can follow links a handful
of established vocabularies and find terms that are not included in
`add_basic_meta`.  For instance, in the `prism` prefix,

@@

we see that there is a term for `modificationDate` for a file.  We create
a `meta` element containing this annotation using the `meta` function:

@@

If we forget to add the namespace with add_meta, we can always add it
later using the `add_namespaces` function,

>>>>

From the list of namespaces in `prefixes`, we can follow links a handful
of established vocabularies and find terms that are not included in
`add_basic_meta`.  For instance, by resolving the location identified
by the `prism` prefix,

@@

we will find that there is a term for `modificationDate` for a file.  We create
a `meta` element containing this annotation using the `meta` function:

@@

<!-- does this mean we can use CURIEs whose prefix has not yet been 
bound to a namespace? that would be bad. there should probably be an
error message when that happens -->
If we forget to add the namespace with add_meta, we can always add it
later using the `add_namespaces` function,
